### First load the dplyr package  
```{r}
library(dplyr)
```

### Download & Extract  
Download the dataset [here](https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip) and extract into a folder name __UCI HAR Dataset__  

### Variables of each data in the dataset  
  + features load the features.txt dataset
  + activities load the activity_labels.txt dataset
  + subject_test load the subject_test.txt dataset
  + x_test load the X_test.txt dataset dataset
  + y_test load the y_test.txt dataset dataset
  + subject_train load the subject_train.txt dataset
  + x_train load the X_train.txt
  + y_train load the y_train.txt dataset
```{r}

```

### Merging all of the dataset in the created variables into a single dataset  
* I used __rbind()__ function to categorize dataset and I used __cbind__ to merge the whole categorized data.  
  + x_train and x_test has been binded and loaded into __x_data__ variable
  + y_train and y_test has been binded and loaded into __y_data__ variable
  + subject_train and subject_test has been binded and loaded into __subject_data__ variable
  + I used cbind to merge x_data, y_data, and subject_data into merged_data variable

### Extraction of mean and standard deviation from the measurement  
I used the following code to extract mean and STD from the measurement  
I have extracted the data into the variable Extract_m_s  
+ m is the mean
+ s is the standard deviation
```{r eval=FALSE}
Extract_m_s <- merged_data %>% select(subject, code, contains("mean"), contains("std"))
```

### Using descriptive names and appropriate labels  
+ The column code in Extract_m_s has been changed into __activities__
+ The Acc in column’s name replaced by __Accelerometer__
+ The Gyro in column’s name replaced by __Gyroscope__
+ The BodyBody in column’s name replaced by __Body__
+ The Mag in column’s name replaced by __Magnitude__
+ The character f in column’s name replaced by __Frequency__
+ The character t in column’s name replaced by __Time__

### In the final step, I created the Tidy Data from the dataset I have just worked on
  I used the chain method to chain the functions into a variable Tidy_Data
```{r eval=FALSE}
Tidy_Data <- Extract_m_s %>%
  group_by(subject, activity) %>%
  summarise_all(funs(mean))
write.table(Tidy_Data, "Tidy_Data.txt", row.name=FALSE)
```
