### First load the dplyr package  
```{r}
library(dplyr)
```

```{r, include=FALSE}
# Load the dplyr package
library(dplyr)
# creating a project zip file
project_file <- "project_data.zip"

# Downloading data into the project_file variable.
if (!file.exists(project_file)){
  url_data <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
  download.file(url_data, project_file, method="curl")
}  

# Unzipping the project file to UCI HAR Datset
if (!file.exists("UCI HAR Dataset")) { 
  unzip(project_file)
}
```

### Download & Extract  
Download the dataset [here](https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip) and extract into a folder name __UCI HAR Dataset__  

### Variables of each data in the dataset  
  + features load the features.txt dataset
  + activities load the activity_labels.txt dataset
  + subject_test load the subject_test.txt dataset
  + x_test load the X_test.txt dataset dataset
  + y_test load the y_test.txt dataset dataset
  + subject_train load the subject_train.txt dataset
  + x_train load the X_train.txt
  + y_train load the y_train.txt dataset
```{r, include=FALSE}
features <- read.table("UCI HAR Dataset/features.txt", col.names = c("n","functions"))
activities <- read.table("UCI HAR Dataset/activity_labels.txt", col.names = c("code", "activity"))
subject_test <- read.table("UCI HAR Dataset/test/subject_test.txt", col.names = "subject")
x_test <- read.table("UCI HAR Dataset/test/X_test.txt", col.names = features$functions)
y_test <- read.table("UCI HAR Dataset/test/y_test.txt", col.names = "code")
subject_train <- read.table("UCI HAR Dataset/train/subject_train.txt", col.names = "subject")
x_train <- read.table("UCI HAR Dataset/train/X_train.txt", col.names = features$functions)
y_train <- read.table("UCI HAR Dataset/train/y_train.txt", col.names = "code")
```

### Merging all of the dataset in the created variables into a single dataset  
* I used __rbind()__ function to categorize dataset and I used __cbind__ to merge the whole categorized data.  
  + x_train and x_test has been binded and loaded into __x_data__ variable
  + y_train and y_test has been binded and loaded into __y_data__ variable
  + subject_train and subject_test has been binded and loaded into __subject_data__ variable
  + I used cbind to merge x_data, y_data, and subject_data into merged_data variable
```{r, include=FALSE}
x_data <- rbind(x_train, x_test)
y_data <- rbind(y_train, y_test)
subject_data <- rbind(subject_train, subject_test)
merged_data <- cbind(subject_data, y_data, x_data)
```

### Extraction of mean and standard deviation from the measurement  
I used the following code to extract mean and STD from the measurement  
I have extracted the data into the variable Extract_m_s  
+ m is the mean
+ s is the standard deviation
```{r eval=FALSE}
Extract_m_s <- merged_data %>% select(subject, code, contains("mean"), contains("std"))
```

```{r, include=FALSE}
Extract_m_s <- merged_data %>% select(subject, code, contains("mean"), contains("std"))
```
### Using descriptive names and appropriate labels  
+ The column code in Extract_m_s has been changed into __activities__
+ The Acc in column’s name replaced by __Accelerometer__
+ The Gyro in column’s name replaced by __Gyroscope__
+ The BodyBody in column’s name replaced by __Body__
+ The Mag in column’s name replaced by __Magnitude__
+ The character f in column’s name replaced by __Frequency__
+ The character t in column’s name replaced by __Time__
```{r, include=FALSE}
Extract_m_s$code <- activities[Extract_m_s$code, 2]

names(Extract_m_s)[2] = "activity"
names(Extract_m_s)<-gsub("Acc", "Accelerometer", names(Extract_m_s))
names(Extract_m_s)<-gsub("Gyro", "Gyroscope", names(Extract_m_s))
names(Extract_m_s)<-gsub("BodyBody", "Body", names(Extract_m_s))
names(Extract_m_s)<-gsub("Mag", "Magnitude", names(Extract_m_s))
names(Extract_m_s)<-gsub("^t", "Time", names(Extract_m_s))
names(Extract_m_s)<-gsub("^f", "Frequency", names(Extract_m_s))
names(Extract_m_s)<-gsub("tBody", "Time_Body", names(Extract_m_s))
names(Extract_m_s)<-gsub("-mean()", "Mean", names(Extract_m_s), ignore.case = TRUE)
names(Extract_m_s)<-gsub("-std()", "Standars_Deviation", names(Extract_m_s), ignore.case = TRUE)
names(Extract_m_s)<-gsub("-freq()", "Frequency", names(Extract_m_s), ignore.case = TRUE)
names(Extract_m_s)<-gsub("angle", "Angle", names(Extract_m_s))
names(Extract_m_s)<-gsub("gravity", "Gravity", names(Extract_m_s))

```
### In the final step, I created the Tidy Data from the dataset I have just worked on
  I used the chain method to chain the functions into a variable Tidy_Data
```{r eval=FALSE}
Tidy_Data <- Extract_m_s %>%
  group_by(subject, activity) %>%
  summarise_all(funs(mean))
write.table(Tidy_Data, "Tidy_Data.txt", row.name=FALSE)
```

```{r, include=FALSE}
Tidy_Data <- Extract_m_s %>%
  group_by(subject, activity) %>%
  summarise_all(funs(mean))
write.table(Tidy_Data, "Tidy_Data.txt", row.name=FALSE)
```

### Here is the summary of the Tidy Data
```{r}
Tidy_Data
```